Sparse Representation Approaches for First Stage Retrieval: A Review

### 2021-12-06 src/article.tex
Figure for SPLADE

    \paragraph{Architecture}
    The importance estimation formula Equation (\ref{eqn:sparterm:importance-predictor})
    has been modified by adding a log-saturation effect, in order to prevent the dominance
    of some terms to dominate and naturally ensures sparsity in representations:
    \begin{equation}
        w_j=\sum_{i \in t}log(1+ReLU(w_{ij}))
    \end{equation}

>>>>

    \paragraph{Architecture}
    \begin{figure}[h]
        \centering
        \def\svgwidth{\columnwidth}
        \input{SPLADE.pdf_tex}
        \caption{Final representation calculation with log saturation}
        \label{fig:SPLADE}
    \end{figure}
    The importance estimation formula Equation (\ref{eqn:sparterm:importance-predictor})
    has been modified by adding a log-saturation effect (Figure \ref{fig:SPLADE}), in order to
    prevent the dominance of some terms to dominate and naturally ensures sparsity in
    representations:
    \begin{equation}
        w_j=\sum_{i \in t}log(1+ReLU(w_{ij}))
    \end{equation}
